\mytitle

### 2021-12-20 paper.tex
extend conclusion

\newcommand{\mytitle}{Comparisons of methods for the calculation of the real dilogarithm regarding instruction-level parallelism}
\newcommand{\myauthor}{Alexander Voigt}
\newcommand{\Li}{\operatorname{Li}_2}
\newcommand{\secref}[1]{Section~\ref{#1}}
\newcommand{\tabref}[1]{\tablename~\ref{#1}}

@@

C, C++ and FORTRAN implementations of the presented algorithm can be
found in the Polylogarithm library \cite{polylogarithm}.
Implementations in Julia and Rust can be found in \cite{PolyLog.jl}
and \cite{polylog}, respectively.

>>>>

\newcommand{\mytitle}{Comparison of methods for the calculation of the real dilogarithm regarding instruction-level parallelism}
\newcommand{\myauthor}{Alexander Voigt}
\newcommand{\Li}{\operatorname{Li}_2}
\newcommand{\secref}[1]{Section~\ref{#1}}
\newcommand{\tabref}[1]{\tablename~\ref{#1}}

@@

In this paper different approaches for the numerical calculation of
the real dilogarithm have been compared w.r.t.\ their potential for
the use of instruction\-/level parallelism.  A particular
implementation of a rational minimax approximant has been proposed and
compared to several existing implementations w.r.t.\ runtime.  C, C++
and FORTRAN implementations of the presented algorithm can be found in
the Polylogarithm library \cite{polylogarithm}.  Implementations in
Julia and Rust can be found in \cite{PolyLog.jl} and \cite{polylog},
respectively.
